Variable Density Tesseroids: Gravity fields calculation in spherical coordinates using variable densities in depth

### 2017-08-25 manuscript/manuscript.tex
Fixed mistake with a plus sign in \ell
Added disable option in new line of todonotes

\usepackage[utf8]{inputenc}
\usepackage{timet}
\usepackage{amsmath}
\usepackage{graphicx}
\usepackage{todonotes} % to make annotations on margins

@@

The integrals that define the gravity fields in equations \ref{eq:tesseroid-pot}-\ref{eq:tesseroid-tensor} have analytical solutions for the exceptional case of a spherical shell with homogeneous density \citep{Mikuska2006,Grombein2013}.
\citet{Uieda2016} and \citet{Grombein2013} compared their numerical models (tesseroids with homogeneous density) with these analytical solutions in order to test the accuracy of their approximations.

@@

\begin{equation}
    \cos\psi = \sin\phi', \quad
    \ell = \sqrt{r'^2 + 2 r r' \sin\phi' + r^2}.
\end{equation}

@@

\begin{equation}
    V_\text{sh}(r) = 2\pi G 
    \int\limits_{-\frac{\pi}{2}}^\frac{\pi}{2}
    \int\limits_{R_1}^{R_2}
    \frac{\rho(r') {r'}^2 \cos\phi'}{\sqrt{r'^2 + 2 r r' \sin\phi' + r^2}}
    \, dr' d\phi',
\end{equation}

>>>>

\usepackage[utf8]{inputenc}
\usepackage{timet}
\usepackage{amsmath}
\usepackage{graphicx}
\usepackage{todonotes} % to make annotations on margins
%~ \usepackage[disable]{todonotes} % to disable annotations on margins

@@

The integrals that define the gravity fields in equations \ref{eq:tesseroid-pot}-\ref{eq:tesseroid-tensor} have analytical solutions for the exceptional case of a spherical shell with homogeneous density \citep{Mikuska2006,Grombein2013}.
In order to test the accuracy of their approximations, \citet{Uieda2016} and \citet{Grombein2013} compared their numerical models (tesseroids with homogeneous density) with these analytical solutions.

@@

\begin{equation}
    \cos\psi = \sin\phi', \quad
    \ell = \sqrt{r'^2 - 2 r r' \sin\phi' + r^2}.
\end{equation}

@@

\begin{equation}
    V_\text{sh}(r) = 2\pi G 
    \int\limits_{-\frac{\pi}{2}}^\frac{\pi}{2}
    \int\limits_{R_1}^{R_2}
    \frac{\rho(r') {r'}^2 \cos\phi'}{\sqrt{r'^2 - 2 r r' \sin\phi' + r^2}}
    \, dr' d\phi',
\end{equation}
